Predicting sales of newly published books

### 2015-08-17 paper.tex
arreglando la introducción

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales.

In this sense, the publishing industry is based on very particular and
established production process, and publishing a book requires several
steps, between which the distribution is important and plays an
important role. 
The publishing process and individual decisions at each step are very
important. 
% One of those decisions is the number of copies to print. 
  % ¿Esto que tiene que ver con la frase anterior? - JJ
Thus, a suitable prediction system for new books should take into
account many details about how the editorial process works. % y? - JJ

Implementing a good forecasting tool requires not only a good study of
the state of the art in this field, but also an accurate knowledge of
the operations and challenges facing the publishing industry and its
supply chain. % ¿eso es lo que vamos a hacer? - JJ

% introducirlo diciendo... El problema de la industria similar es
% parecido a otras industrias, etc, etc...
In the field of fashion predicting sales is very complex problem, subject
to certain requirements \cite{SThomassey2014} and has been faced using
various methods in recent decades
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.  % Este
                                % párrafo no dice absolutamente nada
                                % ni aporta nada. Si se menciona la
                                % industria de la moda, es que vamos a
                                % aprender algo de ella. ¿Cuáles son
                                % los requisitos? ¿Cuáles son los
                                % métodos? ¿Vamos a aprender de ellos?
                                % - JJ

In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. Thus, it is extremely important to
forecast the sales a new book might achieve. % Hala, otro salto. ¿Qué
                                % tiene que ver esto con el párrafo
                                % anterior? - JJ

Thus, using a predictive tool is very useful when used properly; in
this sense, it is very important to know the product, the
characteristics of sales and how to distribute it, as those details
affect the process \cite{Armstrong2001,SThomassey2014}. % ¿Esto
                                % también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ

Book sales are influenced by various factors that make
them fluctuate.  These factors are usually not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy \cite{Little1998}. 
  % ¿Qué hacen todas estas cosas? ¿Vamos a tenerlas en cuenta?

Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}.

Publishers generally use historical data and an expert analyzes that
data and applies his knowledge using external variables to obtain quite
appropriate predictions. % ¿cita para esto?  - JJ
However, in recent years the sales are forecasted using an
application. % ¿Cita para esto? - JJ
This is used as the foundation over which an expert applies his
knowledge, as the company might require an interpretable and
understandable model. For example, the expert might increase or
decrease the sales prediction based on season or sales period.
However, the obtained analysis can be imprecise and may not take all
the variables into account. 
In addition, the process is often tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set. % We NEED a reference for this!!! - JJ

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
properly.

Using predictive tools can benefit a publishing company to optimize 
production and improve their profits or minimize losses \cite{Zhao2001}. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the new book publishing
problem, % no es el problema de publicación, es el problema de venta
         % de libros sin publicar. Habrá que buscar un nombre - JJ
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  
Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{State of the art}
\label{sec:soa}

In the literature several proposals to perform the prediction of sales
in different areas can be found.  %frase que no dice nada. ¿Por qué no
                                %empiezas enmarcando el estado del
                                %arte? Methods to predict book sales
                                %have been generally based on ... - JJ
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods are based on using
historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

Using time series prediction methods is perhaps the most used
technique to tackle the sales forecasting task. 
In this sense, among the most popular techniques include 
statistical techniques \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. 
However, the efficiency of these techniques depends largely on the field of application and the problem data. 
Specifically, techniques that require a large amount of data for predicting sales of new products are not the most suitable for this task \cite{ChingChin2010}.

Anyway, several studies have demonstrated that improving sale predictions (a reduction of forecasting errors) results in an improvement in the production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.

Finally, in many cases the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions \cite{Lapide1999,ChernWSF15}.
In this sense, some authors propose reducing variations in the data caused by such variables to improve the accuracy of predictions
 \cite{Sheikh2003,Schrieber2005}.

Taking into account the kind of problem we address in this paper, the classical forecasting methods are not useful. 
Thus, we must analyze raw data using other tools, prior to apply forecasting techniques.
In addition, since publishers need models to explain obtained predictions, black box forecasting methods may not be suitable for this problem.

@@

Sales forecasting in editorial industry is a very complex
problem. %hala, vuelta la burra al trigo - JJ
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

@@

 % [Pedro] los resultados aún no están terminados de calcular. Pongo
 % unos números cualquiera.
% ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a
% seleccionar uno? - JJ
Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
\hline
  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by SIPESCA (Programa Operativo
FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). % ¿Y el contrato con Trevenque?  - JJ

>>>>

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

% In this sense, the publishing industry is based on very particular and
% established production process, and publishing a book requires several
% steps, between which the distribution is important and plays an
% important role. The publishing process and individual decisions at each step are very
% important. One of those decisions is the number of copies to print. 
  % ¿Esto que tiene que ver con la frase anterior? - JJ
% Thus, a suitable prediction system for new books should take into
% account many details about how the editorial process works. % y? - JJ

% Implementing a good forecasting tool requires not only a good study of
% the state of the art in this field, but also an accurate knowledge of
% the operations and challenges facing the publishing industry and its
% supply chain. % ¿eso es lo que vamos a hacer? - JJ

In the field of publishing industry, it is more important printing an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...

However, accurately using a predictive tool is a difficult task as
book sales are influenced by various factors that make
them fluctuate and usually they might be not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight
traffic, and others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}.

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analized historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, an expert applies his knowledge, as the company might require an interpretable and understandable model.

However, carrying out the analysis and forecasting process as described,
may lead to an imprecise analysis and may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
properly and in an automatic way.

With this in mind, i this paper a data visualization and preprocessing strategy to find
out what are the relevant variables describing a book in the prediction 
of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print roll.

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  
Section \ref{sec:experiments} reports and analyzes the obtained results with a real data set.
Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{Sales forecasting. State of the art}
\label{sec:soa}

In the literature several proposals to perform the prediction of sales
in different fields can be found. % frase que no dice nada. ¿Por qué no empiezas enmarcando el estado del
                                % arte? Methods to predict book sales have been generally based on ... - JJ
                                % [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
                                %  por eso quiero enfocarlo desde el punto de vista de la predicción 
                                %  de ventas en general, que sí hay bastante en muchos campos.
On the one hand, several qualitative methods are based on an expert
experience, while time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
are based on using historical data to make predictions
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. % Hasta ahora no has
                                % dicho cuál es el problema. Tienes
                                % que decir claramente qué tienes y
                                % qué quieres. - JJ

Although using time series prediction methods is perhaps the most used
technique to tackle the sales forecasting task, the efficiency of these 
techniques depends largely on the field of application and the problem data. 
Specifically, techniques that require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

Thus, in the last years, different analysis and forecasting methods 
have been proposed for sales forecasting in several industry fields. %similar to the publishing industry.

  %[Pedro] el caso de la industria de la moda es muy similar al de la 
  % publicación de nuevos libros, ya que no hay datos históricos 
  % de un nuevo producto, y hay que echar mano de productos similares
  % o simplemente de los datos que describen el nuevo producto.
In the fashion industry, very similar to the publishing industry, 
predicting sales is a very complex problem, subject
to certain specific requirements \cite{SThomassey2014}.
This task has been faced using various methods in recent decades
  %[Pedro] me falta describir las aproximaciones
\cite{Thomassey2012,Xia2012,Hammond1990,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre
  % New tea product
  % New cosmetic product
  % New soft drink product

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre 
  % sales forecasting in printed circuit board industry

Finally, in many cases the predictions are influenced by external 
variables that must be taken into account, such as seasonality, 
promotions or fashions \cite{Lapide1999,ChingChin2010,ChernWSF15}.
In this sense, some authors propose reducing variations in the data 
caused by such variables to improve the accuracy of predictions
 \cite{Sheikh2003,Schrieber2005}.

%On the other hand, different authors have proposed metrics to determine the accuracy of estimates. 
%However, most companies use metrics based on the analysis of errors (MSE, MAPE) \cite{ChingChin2010,Madsen2008}.

Taking into account the kind of problem we address in this paper, the 
classical forecasting methods are not useful. 
Thus, we must analyze raw data using other tools, prior to apply 
forecasting techniques.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are proposed.

@@

%Sales forecasting in editorial industry is a very complex problem. 
        %hala, vuelta la burra al trigo - JJ
        %[Pedro] ea, lo quito
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

  %[Pedro] me falta poner ya los nombres traducidos (y usarlos para los SOM)

@@

  %[pedro] los resultados aún no están terminados de calcular. Pongo unos números cualquiera.
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados.
Obtained results using the different forecasting methods on the dataset with 13 variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	& MAE 			& RMSE 			& RAE 			& RRSE 			\\
\hline
  MP5 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  LR 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  SVM 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  KNN 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
  MLP 		& 35 $\pm$ 1 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	& 20 $\pm$ 2 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by PreTEL (PRM Consultores - Trevenque),
SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 and
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). 
    % ¿Y el contrato con Trevenque?  - JJ
    %[pedro] añadido
